### 2025-02-21 introduction.tex
new

Successful risk management practice can enhance financial stability and resilience for individual companies and for the financial system too.

@@

Chapter~\ref{chap:project2 } also includes sensitivity testing of the neural network metamodel.

@@

Chapter~\ref{chap:futureWork } explores future applications of deep reinforcement learning in the dynamic hedging of VA contracts.

\section{Managing Risk of Variable Annuity with Nested Simulation}

@@

In the subsequent chapters, we dive deeper into these topics.
Chapter~\ref{chap:project1} provides a comprehensive analysis of the convergence properties of existing nested simulation procedures and their practical implications.
Chapter~\ref{chap:project2} focuses on the development and evaluation of neural network metamodels, particularly LSTM networks, for enhancing the efficiency of nested simulations in risk management of VA contracts.
We also examine the robustness and generalization capabilities of these models in the presence of simulation noise.
Chapter~\ref{chap:project3} explores the use of transfer learning techniques to adapt neural network metamodels to new market conditions and contract specifications.
Our approach enables rapid deployment in changing environments.
Finally, Chapter~\ref{chap:conclusion} summarizes the key findings of this thesis and discusses future research directions that involve the robost use of neural networks in quantitative risk management applications.

>>>>

Successful risk management practice can enhance financial stability and resilience for individual companies and for the financial system as well.

@@

Chapter~\ref{chap:project2} also includes sensitivity testing of the neural network metamodel.

@@

Chapter~\ref{chap:futureWork} explores future applications of deep reinforcement learning in the dynamic hedging of VA contracts.

\section{Risk Management of Variable Annuities with Nested Simulation}

@@

In the subsequent chapters, we dive deeper into these topics.
Chapter~\ref{chap:project1} provides a comprehensive analysis of the convergence properties of existing nested simulation procedures and their practical implications.
Chapter~\ref{chap:project2} focuses on the development and evaluation of neural network metamodels, particularly LSTM networks, for enhancing the efficiency of nested simulations in risk management of VA contracts.
We also examine the robustness and generalization capabilities of these models in the presence of simulation noise.
Chapter~\ref{chap:project3} explores the use of transfer learning techniques to adapt neural network metamodels to new market conditions and contract specifications.
Our approach enables rapid deployment in changing environments.
Chapter~\ref{chap:conclusion} summarizes the key findings of this thesis and discusses future research directions that involve the robost use of neural networks in quantitative risk management applications.
Chapter~\ref{chap:futureWork} explores future applications of transfer learning and deep reinforcement learning in the dynamic hedging of VA contracts.
